### 2023-09-11 main.tex
lkj

Describe eigenvalues of $T_0$ following 
\cite{Belliard2} 
\section{Extensions for the non-integrable chain}
In Sections \ref{sectionIntegrabiliy} and \ref{Section-Mapping} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable thanks to integrability. This nice property is lost when we allow an arbitrary maximal occupation $\nu>1$, therefore it is natural to ask if we can still say something about correlations. Again, exploiting duality, steady state correlations can be expressed in terms of absorption probabilities of the dual particles. Moreover, the thermalized process can be studied, by finding the thermalization measure and the dual-thermalized process. Finally, a reaction can be added by conserving the same duality function. 
\subsection{Steady state correlations and duality}

@@

The dual generator is 

@@

@@

		\sum_{i_{1}=0}^{|\xi_{1}|}\ldots\sum_{i_{N}=0}^{|\xi_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{i_{a}}\left(\rho_{a}^{R}\right)^{|\xi_{a}|-i_{a}}a_{i_{1},\ldots,i_{N}}(\bm{\xi})

@@

	a_{i_{1},\ldots,i_{N}}(\bm{\xi})=\mathbb{P}\left(\xi(\infty)=\sum_{a=1}^{N-1}\left(i_{a}\delta_{0}+(|\xi_{a}|-i_{a})\delta_{L+1}\right)| \xi_{0}=\xi\right)
where $D(\bm{n},\bm{\xi})$ is the duality function defined in \eqref{dualityFunctionChain}. Here, we denote by $|\xi_{a}|=\sum_{x=1}^{L}\xi_{a}^{x}$ and by $i_{a}$ the number of dual particles of species $a\in\{1,\ldots,N-1\}$ absorbed at left, thus we denote by $|\xi_{a}|-i_{a}$ the number of particles of the same type absorbed at right.\\
We observe that the duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\widehat{\xi}}=\delta_{\tau_{1}}^{y_{1}}+\ldots+\delta_{s_{m}}^{y_{m}}$ with $y_{x}<y_{x+1}$ $\forall x\in \{1,\ldots,m-1\}$ and $s_{x}\in \{1,\ldots,N-1\}$ $\forall x=\{1,\ldots,m\}$ is given by 
	D(\bm{n},\bm{\widehat{\xi}})= \frac{\prod_{x=1}^{m}n_{s_{a}}^{y_{x}}}{(\nu-m+1)}
Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\widehat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations between non-empty species of types $s_{i}\in\{1,\ldots,N-1\}$ situated at sites $y_{x}\in\{1,\ldots,L\}$ with $x\in \{1,\ldots,m\}$. This expectation is computed by \eqref{ExptationSS} once the absorption probabilities is known. The issue is that, usually, these absorption probabilities fulfil some difference equations that are not easy to solve. For example, we report here the solution for the one points correlations. 

@@

@@

		\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{s}^{x})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\rho_{s}^{L}\right)^{i_{s}}\left(\rho_{s}^{R}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)
we want to determine $a^{x}_{s}(1)=\mathbb{P}_{\delta_{s}^{x}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$ is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries. Therefore, this $a_{s}^{x}(1)$ fulfils the following equations 

@@

		a^{1}_{s}(1)=\frac{|\alpha|}{1+|\alpha|}+a^{2}_{s}(1)\frac{1}{1+|\alpha|}\\
		a^{L}_{s}(1)=a^{L-1}_{s}(1)\frac{1}{1+|\beta|}

@@

where $\Delta_{x}^{L}$ is the discrete Laplace operator on the chain of length $L$ and where. The equations \eqref{gamblers-ruin} can be solved.Therefore, using \eqref{OnePtsCORR} and $a^{x}_{s}(0)=1-a^{x}_{s}(1)$ we obtain 

@@

\subsection{Instantaneous thermalization}

@@

	\epsilon_{1}=2\nu-\sum_{a=2}^{N}\epsilon_{a}\qquad r_{1}=\nu-\sum_{a=2}^{N}r_{a}

@@

	\mathcal{L}_{x,x+1}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{n_{1}^{x}+n_{1}^{x+1}}\ldots\sum_{r_{N}=0}^{n_{N}^{x}+n_{N}^{x+1}}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}\}}

@@

		\mathcal{L}_{left}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}\}}\left\{f(\bm{r},n^{2},\ldots,n^{L})-f(\bm{n})\right\}\\&
		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}

@@

	D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\left(\rho_{a}^{L}\right)^{\xi_{a}^{0}}\prod_{x=1}^{L}\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\prod_{a=2}^{N}\left(\rho_{a}^{R}\right)^{\xi_{a}^{L+1}}
The proof of the duality consists in proving 

@@

	d_{x}(n^{x},\xi^{x}):=\frac{(\nu-\sum_{a=2}^{N}\xi_{a}^{x})!}{\nu!}\prod_{a=2}^{N}\frac{\eta_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}

@@

	\left(\mathcal{L}_{left}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})=\nonumber&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=2}^{N}\xi_{c}^{1}\right)!}{\nu!}\right.

@@

	\left.\prod_{b=2}^{N}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}

@@

	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}
Multiplying by $\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{-r_{a}+r_{a}-\xi_{a}^{1}+\xi_{a}^{1}}$ and using the Multinomial Theorem we have that the first addend in the curly brackets is

@@

	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=2}^{N}\xi_{c}^{1}\right)!}{\nu!}\right.\nonumber

@@

	\left.\prod_{b=2}^{N}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}\right\}	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}\\=&
	\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}
Multiplying by $\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}$ and by the multinomial Theorem, we have that the second addend in the curly bracket is

@@

	&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=2}^{N}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}\prod_{a=2}^{N}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}\\=&D(\bm{n},\bm{\xi})

@@

	\left(\mathcal{L}_{left}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left\{\prod_{a=2}^{N}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=2}^{N}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}

@@

\subsection{Multi-species stirring process with reaction}

>>>>

Describe eigenvalues of $T_0$ following 
\cite{Belliard2} 
\section{Extensions for the non-integrable chain}
The aim of this section is studying some extension to the analysis previously done when integrability property is lost. 
In particular, Sections \ref{sectionIntegrabiliy} and \ref{Section-Mapping} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable thanks to integrability.  
This nice property is lost when we allow an arbitrary maximal occupation $\nu>1$. For the sake of simplicity we still study the geometry of chain and we provide the following extensions: 
\begin{enumerate}
	\item \textit{Arbitrary correlations}: exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles. These probability are hard to find in this partial exclusion situation, however correlation can be formally written. Subsection \ref{Subsection-ss-nonI}.
	\item \textit{Instantaneous thermalization}: starting from the multi-species stirring dynamics, we can define the thermalized process, where particle are redistribute in each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond. Subsection \ref{Subsection-Thermalized}.
	\item \textit{Reaction-diffusion process}: a further dynamics is added. Particle can now change type. The model is constructed with the goal of having the average density evolving a system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}. Subsection \ref{Subsection-RD}
\end{enumerate}

\subsection{Steady state correlations and duality}\label{Subsection-ss-nonI}

@@

whit dual generator

@@

The dual process has absorbing boundaries, i.e. all dual particles are eventually absorbed at $0$ or at $L+1$ with a certain probability. This implies that, the chain is eventually void and the steady state correlation of the original process can be written via the absorption probabilities of the dual process as explained in the following. 
We call $\mu_{stat}$ the stationary measure of the the process $(\bm{n}(t))_{t\geq 0}$. We assume that it is initially distribute with a configuration $\bm{n}$. For every $m\in\{1,\ldots,L\}$ we consider the dual configuration  $\bm{\widehat{\xi}}=\delta_{\tau_{1}}^{y_{1}}+\ldots+\delta_{s_{m}}^{y_{m}}$ with $y_{x}<y_{x+1}$  and $s_{x}\in \{1,\ldots,N-1\}$ for every $x\in \{1,\ldots,m-1\}$. The following chain of equalities holds

@@

		\mathbb{E}_{\mu^{stat}}\left[D(\bm{n}(t),\hat{\bm{\xi}})\right]&=\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\hat{\bm{\xi}})\right]=\lim_{t\to\infty}\mathbb{E}_{\hat{\bm{\xi}}}\left[D(\bm{n},\bm{\xi}(t))\right]
		\sum_{i_{1}=0}^{|\hat{\xi}_{1}|}\ldots\sum_{i_{N}=0}^{|\hat{\xi}_{N}|}\prod_{a=1}^{N-1}\left(\rho_{a}^{L}\right)^{i_{a}}\left(\rho_{a}^{R}\right)^{|\hat{\xi}_{a}|-i_{a}}\mathcal{P}(i_{1},\ldots,i_{N},\hat{\bm{\xi}})

@@

\mathcal{P}(i_{1},\ldots,i_{N},\hat{\bm{\xi}})	=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{a=1}^{N-1}\left(i_{a}\delta_{0}+(|\hat{\xi}_{a}|-i_{a})\delta_{L+1}\right)| \bm{\xi_{0}}=\hat{\bm{\xi}}\right)
and where $D(\bm{n},\bm{\xi})$ is the duality function defined in \eqref{dualityFunctionChain}. Here, we denote by $|\hat{\xi}_{a}|=\sum_{x=1}^{L}\hat{\xi}_{a}^{x}$ and by $i_{a}$ the number of dual particles of species $a\in\{1,\ldots,N-1\}$ absorbed at left, thus we denote by $|\hat{\xi}_{a}|-i_{a}$ the number of particles of the same type absorbed at right.\\
The duality function \eqref{dualityFunctionChain} computed in the dual configurations $\bm{\hat{\xi}}$ is given by 
	D(\bm{n},\bm{\hat{\xi}})= \frac{\prod_{x=1}^{m}n_{s_{a}}^{y_{x}}}{(\nu-m+1)}
Therefore, up to a constant, $\mathbb{E}_{\mu^{\text{stat}}}\left[D(\bm{n},\bm{\hat{\xi}})\right]$ gives the non-equilibrium stationary state $m-$points correlations between non-empty species of types $s_{i}\in\{1,\ldots,N-1\}$ situated at sites $y_{x}\in\{1,\ldots,L\}$ with $x\in \{1,\ldots,m\}$. This expectation is computed by \eqref{ExptationSS} once the absorption probabilities is known. The issue is that these absorption probabilities fulfil some difference equations that are not easy to solve. For example, we report here the solution for the one points correlations. 

@@

We have that $\widehat{\bm{\xi}}=\delta_{s}^{y}$, then 
	\nu D(\eta,\delta_{s}^{y})=n_{s}^{y}

@@

		\langle n_{s}^{x}\rangle_{\text{stat}}&=\frac{1}{\nu}\lim_{t\to\infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\delta_{s}^{y})\right]\\&=\frac{1}{\nu}\sum_{i_{s}=0}^{1}\left(\rho_{s}^{L}\right)^{i_{s}}\left(\rho_{s}^{R}\right)^{1-i_{s}}\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)
we want to determine $\mathcal{P}(1,\delta_{s}^{y})=\mathbb{P}_{\delta_{s}^{y}}\left(\xi_{\infty}=i_{s}\delta_{0}+(1-i_{s})\delta_{L+1}\right)$ is the probability of a random walker on the chain $\{1,\ldots,L\}$ with absorbing boundaries. Therefore, this $\mathcal{P}(1,\delta_{s}^{y})$ fulfils the following equations 

@@

		\Delta_{x}^{L}\mathcal{P}(1,\delta_{s}^{y})=0\\
		\mathcal{P}(1,\delta_{s}^{1})=\frac{|\alpha|}{1+|\alpha|}+\mathcal{P}(1,\delta_{s}^{2})\frac{1}{1+|\alpha|}\\
	\mathcal{P}(1,\delta_{s}^{L})=\mathcal{P}(1,\delta_{s}^{L-1})\frac{1}{1+|\beta|}

@@

where $\Delta_{x}^{L}$ is the discrete Laplace operator on the chain of length $L$. The equations \eqref{gamblers-ruin} can be solved. Therefore, using \eqref{OnePtsCORR} and $\mathcal{P}(1,\delta_{s}^{y})=1-\mathcal{P}(0,\delta_{s}^{y})$ we obtain 

@@

\subsection{Instantaneous thermalization}\label{Subsection-Thermalized}

@@

	\epsilon_{N}=2\nu-\sum_{a=1}^{N-1}\epsilon_{a}\qquad r_{1}=\nu-\sum_{a=1}^{N-1}r_{a}

@@

	\mathcal{L}_{x,x+1}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{n_{1}^{x}+n_{1}^{x+1}}\ldots\sum_{r_{N}=0}^{n_{N}^{x}+n_{N}^{x+1}}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}

@@

		\mathcal{L}_{left}^{TH}f(\bm{n})=&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{f(\bm{r},n^{2},\ldots,n^{L})-f(\bm{n})\right\}\\&
		\binom{\nu}{r_{1},\ldots, r_{N}}\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}

@@

The proof of the duality consists in showing

@@

	d_{x}(n^{x},\xi^{x}):=\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}

@@

	\left(\mathcal{L}_{left}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})=\nonumber&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\right.

@@

	\left.\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}

@@

	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}
Multiplying by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{-r_{a}+r_{a}-\xi_{a}^{1}+\xi_{a}^{1}}$ and using the Multinomial Theorem we have that the first addend in the curly brackets is

@@

	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\right.\nonumber

@@

	\left.\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}\right\}	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu-\xi_{k}^{1}+\xi_{k}^{1}-r_{a}+r_{a}}\\=&
	\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}
Multiplying by $\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}$ and by the multinomial Theorem, we have that the second addend in the curly bracket is

@@

	&D(\bm{n},\bm{\xi})\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{1}}\right)^{r_{k}}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{\nu}\prod_{a=1}^{N-1}\left(\frac{\alpha_{1}}{|\alpha|}\right)^{r_{a}-r_{a}}\\=&D(\bm{n},\bm{\xi})

@@

	\left(\mathcal{L}_{left}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}

@@

\subsection{Multi-species stirring process with reaction} \label{Subsection-RD}
